Title here

### 2016-12-06 portfolio/text/ms.Rmd
Keep editing results

Trends in fishing revenue and diversification over time for individuals fishing
commercially in Alaska (Fig. \ref{fig:ts}A) reveal a transition toward
specialization, and in particular specialization on fishing salmon. The majority
(70--90%) of fishers hold single permits, with a slight increase in
single-permit holders since ~2000 (Fig. \ref{fig:ts}C). This overall trend is
most sensitive to halibut or salmon permit holders --- compared to other
fisheries, halibut permit holders are more likely to hold multiple permits
whereas salmon permit holders are more likely to be single permit holders (Fig.
\ref{fig:ts}C). Despite making up only 10--30% of the individuals, multiple
permit holders make approximately half the overall revenue (Fig. \ref{fig:ts}B).
The mean fished species diversity of this revenue declined somewhat from
1980--2000 but has since remained steady (Fig. \ref{fig:ts}D). However, this
trend appears to be driven by an increase in salmon specialists in the 1980s and
1990s --- the trend disappears if salmon license holders are excluded (Fig.
\ref{fig:ts}D).

We observe a clear exponential decrease in revenue variability for strategies
(groups of permits) with higher mean fished species diversity (Fig.
\ref{fig:across}). Strategies with one unit higher mean effective species
diversity had on average `r h1[[2]]`% (`r h1[[1]]`--`r h1[[3]]`% 95% CI) lower
standardized variability. This pattern looks qualitatively similar with or
without individuals targeting salmon. The gillnet fishery for herring roe and
the king crab fishery had the highest estimated revenue variability. Most of the
strategies with the lowest estimated revenue variability combined halibut with
a salmon permit and had high levels of fished species diversity (Fig.
\ref{fig:across}).

Comparing single permit holders to other individuals holding that same permit
plus one or more other permits illustrates the expected reduction in revenue
variability from purchasing additional permits (Fig. \ref{fig:spokes}, Fig.
S\ref{fig:spoke-all}). For example, individuals fishing a halibut longline
permit plus one additional permit always had lower expected revenue variability
compared to individuals fishing only a halibut longline permit (median reduction
of `r 100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`% IQR], Fig.
\ref{fig:spokes}A). Likewise, adding a permit to a herring roe gillnet strategy
substantially reduced expected revenue variability (Fig. \ref{fig:spokes}B).
Adding permits also usually resulted in higher expected revenue, although the
permits themselves represent a significant expense (e.g. XX).

>>>>

We evaluated trends in revenue and diversification over time for individuals
fishing commercially in Alaska from 1985--2014 (Fig. \ref{fig:ts}A). The
majority (70--90%) of fishers hold single permits, with a slight increase in
single-permit holders since 2000 (Fig. \ref{fig:ts}C). This overall trend is
most sensitive to halibut or salmon permit holders --- compared to other
fisheries, halibut permit holders are more likely to hold halibut plus other
permits, whereas salmon permit holders are more likely to hold only one permit
(Fig. \ref{fig:ts}C). Despite making up only 10--30% of the individuals,
multiple permit holders make approximately half of the overall revenue (Fig.
\ref{fig:ts}B). The mean effective fished species diversity of this revenue
declined somewhat from 1980--2000 but has since remained steady (Fig.
\ref{fig:ts}D). However, this trend appears to be driven by an increase in
salmon specialists in the 1980s and 1990s --- the trend disappears if salmon
license holders are excluded (Fig. \ref{fig:ts}D).

Revenue variability decreases exponentially with higher mean fished species
diversity across permit sets (Fig. \ref{fig:across}). Controlling for effort,
strategies with one unit higher mean effective species diversity had on average
`r h1[[2]]`% (`r h1[[1]]`--`r h1[[3]]`% 95% CI) lower variability. This pattern
looks qualitatively similar with or without individuals targeting salmon. As
examples, variability was highest for the herring roe gillnet and king crab
fisheries. Most of the strategies with the lowest estimated revenue variability
combined halibut with a salmon permit and had high levels of fished species
diversity (Fig. \ref{fig:across}).

Comparing single permit holders to individuals holding that same permit plus
additional permits illustrates the expected reduction in revenue variability
from purchasing additional permits (Fig. \ref{fig:spokes}, Fig.
S\ref{fig:spoke-all}). For example, individuals fishing a halibut longline
permit plus one additional permit always had lower expected revenue variability
compared to individuals fishing only a halibut longline permit (median reduction
of `r 100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`% IQR], Fig.
\ref{fig:spokes}A). Likewise, adding a permit to a herring roe gillnet strategy
substantially reduced expected revenue variability (Fig. \ref{fig:spokes}B).
Adding permits also usually increased expected revenue, although the permits
themselves represent a significant expense (e.g. TODO).
